---
title: "Dads are weird"
author: "Ashmita Biswas"
---
Are Dad's weird?


## About the Data 

This data set is derived from the peasants of Manipal University to analyse the ratings of classic tv series - Friends, Modern Family, and Big Bang Theory

## Data Dictionary

:   **gender:** Gender of the student where, categorized by 'Male' and 'Female'

:   **college:** Institute within Manipal University, the peasant belongs to.

:   **is_dad_weird:** Is the dad perceived as weird or not, categorized by 'Yes' and 'No'

:   **name:** Name of the student (aka. peasant)


## Hypothesis

- Do SMI students find their dads to be weirder as compared to MIT

- Is there a bias in gender when it comes do dad weirdness perception of dads.

### Setup

```{r}
#| label: setup
#| echo: false

library(readr)
library(tidyverse)
library(ggformula)
library(mosaic)
library(skimr)
library(visdat) 
library(naniar)
library(janitor)
library(tinytable)
library(DT)
library(crosstable)
library(geofacet)
library(ggplot2)
library(GGally)
```

### Reading the Data

```{r}

weird_dad_data <- read_csv("~/Documents/R_work/Class work 2/ClassWork2/posts/A3/Datasets for A3/3-weird_dads.csv") %>%
janitor::clean_names(case = "snake")
weird_dad_data
```
