---
title: "Weekly Expenditure"
author: "Ashmita Biswas"
---

# Weekly expenditure

How much do Srishti students spend in a week?

## About the Data

This data set is derived from the peasants of Srishti Manipal Institute to analyse the spending behaviour in a week.

## Data Dictionary


:   **Name:** Name of the student

:   **Gender:** Gender of the students categorized as 'Male' & 'Female'

:   **Total_Expenditure_Last_Week:** Total amount of money spent in the last week by the student

## Hypothesis

-  Will Friends have significantly higher ratings than Big Bang Theory due to broader cultural popularity and peer influence?


- Is there a difference in spending behaviour amongst the different gender?


### Setup

```{r}
#| label: setup
#| echo: false

library(readr)
library(tidyverse)
library(ggformula)
library(mosaic)
library(skimr)
library(visdat) 
library(naniar)
library(janitor)
library(tinytable)
library(DT)
library(crosstable)
library(geofacet)
library(ggplot2)
library(GGally)
```

### Reading the Data

```{r}

weekly_expends_data <- read_csv("~/Documents/R_work/Class work 2/ClassWork2/posts/A3/Datasets for A3/4-weekly_expenditure.csv") %>%
janitor::clean_names(case = "snake")
weekly_expends_data
```
